A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2024-02-18 paper/paper.tex
Fix citation for takahashi

The predicates $[[wne a]]$ and $[[wn
a]]$ describe terms that can evaluate into $\beta$-neutral or
$\beta$-normal form through parallel reduction and are defined as
follows.\scw{What does $[[wne]]$ stand for?}
\[ [[wne a]] \iff \exists [[e]], [[a =>+ e]] \]
\[ [[wn a]] \iff \exists [[f]], [[a =>+ f]] \]

>>>>

The predicates $[[wne a]]$ and $[[wn
a]]$ describe terms that can evaluate into $\beta$-neutral or
$\beta$-normal form through parallel reduction and are defined as
follows.\scw{What does $wne$ stand for?}
\[ [[wne a]] \iff \exists [[e]], [[a =>+ e]] \]
\[ [[wn a]] \iff \exists [[f]], [[a =>+ f]] \]
